Molecular Gas Dynamics of the Strongly-lensed Quasar Host Galaxy RXS J1131$-$1231

### 2016-08-30 WRITEUP/ms.tex
some more rewording from myself

%
% %Tacconi13a: the best-fit MS, SFR would be 12.1 Msun/yr for MS given Mstar = 3e10.
% %sSFR (Gyr^-1) = 0.68 (Mstar/6.6e10)^-0.35((1+z)/2.2)^2.8 = 0.40 if RXJ on MS
The specific star formation rate (sSFR\eq SFR/$M_*$) of 4\petm{2.6}{2.4}\,Gyr\pmOne derived for RXJ1131
is $\lesssim$1.5$\sigma$ above the main sequence according to
the redshift-dependent ``main sequence'' relation in \citet[and references therein]{Tacconi13a}.
%  and is consistent with those of the \cite{dacunha10a} sample of local ULIRGs.
Given that RXJ1131 share similar \SF rate, \SF efficiency, and CO disk size as other ``main sequence'' disk galaxies,
the slight enhancement in sSFR may suggest
that the \SF in RXJ1131 is driven by the interactions with the companion.

@@

Adopting the stellar mass as an upper limit to the bulge mass, we find a
$M_{\rm BH}$$/$$M_{\rm bulge}$$>$0.27\petm{11}{8}\% for  of RXJ1131, providing
a direct constraint on the empirical $M_{\rm BH}$$-$\mbulge relation at $z$\ssim0.65.
The elevated $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio compared to the local relation suggests that the
black hole in RXJ1131 has grown faster or earlier than its host galaxy than nearby AGN host galaxies,
consistent with the results from existing studies of the evolution in the growth of SMBHs and their host galaxies
 \citep[e.g.,][]{Walter04a, Peng06a,McLure06a}.
 The elevated ratio also suggests that the stellar bulge component of RXJ1131 is still assembling in order to evolve onto the local  $M_{\rm BH}$$-$$M_{\rm bulge}$ relation.
 %the ratio is larger at high z than the present day, implying evolution in the Mbh?Msph relation

>>>>

%
% %Tacconi13a: the best-fit MS, SFR would be 12.1 Msun/yr for MS given Mstar = 3e10.
% %sSFR (Gyr^-1) = 0.68 (Mstar/6.6e10)^-0.35((1+z)/2.2)^2.8 = 0.40 if RXJ on MS
The specific star formation rate (sSFR\eq SFR/$M_*$) of 4\petm{2.6}{2.4}\,Gyr\pmOne derived for RXJ1131
is $\lesssim$1.5$\sigma$ above the main sequence according to
the redshift-dependent ``main sequence'' relation in \citet[and references therein]{Tacconi13a}.
%  and is consistent with those of the \cite{dacunha10a} sample of local ULIRGs.
Given that RXJ1131 share similar \SF rate, \SF efficiency, and CO disk size as other ``main sequence'' disk galaxies,
the slight enhancement in sSFR suggests
that the \SF in RXJ1131 may be predominantly driven by interactions with the companion.

@@

Adopting the stellar mass as an upper limit to the bulge mass, we find a
$M_{\rm BH}$$/$$M_{\rm bulge}$$>$0.27\petm{11}{8}\% for RXJ1131, providing
a direct constraint on the empirical $M_{\rm BH}$$-$\mbulge relation at $z$\ssim0.65.
The elevated $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio compared to the local relation suggests that the
black hole in RXJ1131 has grown faster or earlier than its host galaxy than nearby AGN host galaxies,
consistent with the results from existing studies of the evolution in the growth of SMBHs and their host galaxies
 \citep[e.g.,][]{Walter04a, Peng06a,McLure06a}.
 The elevated ratio also suggests that the stellar bulge component of RXJ1131 is still assembling in order to evolve onto the local  $M_{\rm BH}$$-$$M_{\rm bulge}$ relation.
 %the ratio is larger at high z than the present day, implying evolution in the Mbh?Msph relation
